---
title: "Assigment1_Reproducible_Research"
author: "Roxana Niksefat"
date: "2023-11-02"
output: HTML_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading the activity dataset

```{r echo = TRUE }
dat <- read.csv("activity.csv")
```

## cleaning data

```{r echo = TRUE }
dat2 <- na.omit(dat)
```


## Histogram of the total number of steps taken each day

```{r echo = TRUE }
hist(x = dat2$steps,xlab = "number of steps taken each day"
     , ylab = "Freqyency of the number of steps",
     main = "Number of steps histogram",type = "l")
```
## Mean and median number of steps taken each day

```{r echo = TRUE }

meansteps <- mean(dat2$steps)
mediansteps <-median(dat2$steps)
```
## Time series plot of the average number of steps taken

```{r warning = FALSE , echo = TRUE }
plot(dat2$steps, run=TRUE,
     )
```

## The 5-minute interval that, on average, contains the maximum number of steps



## Code to describe and show a strategy for imputing missing data

## Histogram of the total number of steps taken each day after missing values are impute

## Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends



